A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
update beading_transitioning_filtering image

\begin{figure*}
\centering
\setlength{\figwidth}{\textwidth}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
First we initialize the bead counts (black) in the marked regions (blue).
We then extract the anchor locations (purple) of the transitions to a different bead count should be.
We then filter out regions of constant bead count.
We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
Transitioning is robust against small pertuirbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.15\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered}We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}
